Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-21 ijar-npb-ms.tex
Another missed +s !!
comments Frank on secs 1,2 and 8

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

@@

Based on expert assumptions for component failure distribution and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise or interval probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

Our imprecise probability approach leads to sets of system reliability functions,
where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
reflects the precision of the reliability estimate:
a short range will indicate that we can quantify the reliability of the system quite precisely,
while a large range will indicate that our (probabilistic) knowledge is rather shaky --
remember that the reliability function is in essence a collection of probability statements.

@@

As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
ultimately conveying a false sense of certainty
by communicating that we can quantify the reliability of the system quite precisely when in fact we can not.
In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
***This step is less trivial here as we must ensure to have probability distributions for these events,
thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
***covered because of parametric distribution, min and max over parameter sets (see section 6)***
***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
\td{Leave out the sentences framed with `***'?}
Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
to reflect uncertainty about system functioning for known states of its components.
A further suggestion was to generalize this to lower and upper structure functions,
within the theory of imprecise probability \citep{itip,CU11}.
These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
which in the latter case also becomes an imprecise probability.

The survival signature is a powerful but rather basic concept.
As such, further generalizations are conceptually easy,
for example one can straightforwardly generalize the survival signature to multi-state systems
such that it again summarizes the structure function
in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.

@@

The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
enabling diagnoses of prior-data conflict which is consequential at the system
level, via sets of system reliability functions.

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
%
%To see this,
%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%%the posterior parameter set bounds are the transformed prior parameter set bounds,
%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%%
%Now, a higher posterior expected functioning probability means
%higher probability for many components out of $m_k$ surviving,
%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
%such that the cmfs for different values of $\yktn$ do not cross each other.
%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \,, \label{eq:LwrSysPostA}
\end{align}
and similarly maximising for $\uRsys(\cdot)$.

Note that $\Phi(\cdot)$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
thus if there is first-order stochastic ordering on $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$
for each $k$, then this ordering can be used to determine the elements of $\PtZi{k}$
which minimise and maximise the overall system reliability function without
resorting to computationally expensive exhaustive searches or numerical optimisation.

We therefore start by proving the following result, where indices are suppressed for readability.
We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.

\begin{theorem}
  \label{thm:y}
  Let $\beta_y$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $n, m, s,$ and $N$ fixed and unknown.

  Then $\beta_{\yu} \ge_{\mathrm{st}} \beta_{\yl} \ \forall \ \yu > \yl$ with $\yu, \yl \in (0,1)$.
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:y}.

Consequently, for each component, the posterior predictive Beta Binomial distributions 
with larger prior functioning probability stochastically dominate those
with smaller prior functioning probability, providing rigorous proof 
which accords with intuition. Applying this result to the sets of system reliability 
functions, together with the monotonicity in the survival signature, means that
$\lRsys(\cdot)$ is attained when $\yktz = \yktzl$ and $\uRsys(\cdot)$
is attained when $\yktz = \yktzu$ for all possible $\nktz$ values.

The analogous result for $\nktz$ is more subtle, because stochastic 
dominance is not guaranteed at a single value.  The following Theorem 
provides the conditions under which an upper or lower limit has first-order stochastic dominance.

\begin{theorem}
  \label{thm:n}
  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
  with $y, m, s,$ and $N$ fixed and unknown.  
  Then,
  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{theorem}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.

These first-order stochastic domination results now gives the exact 
solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
%For $\lRsys(\cdot)$, the minimum is achieved at
%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
    \nonumber\\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
 &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
   \nktzu & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k < 0 \\
   \nktzl & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k > 0 \\
 \end{aligned} \right. \nonumber
\end{align}

\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}

In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
%***How to choose the sets of priors for the survival function of type $k$ components,
%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***

@@

***Extend the model to deal with right-censored observations which are common in the reliability setting.
We believe that a minimal assumption (component can fail immediately after censoring or live forever)
will be simple to implememt but will lead to high imprecision,
whereas assuming exchangeability with other surviving components at moment of censoring
will be more complex to accomodate but will lead to less imprecision.

@@

\section*{Appendix}
\appendix
\renewcommand*{\thesection}{\Alph{section}}

\section{Proofs}
\label{ap:proofs}

\begin{proof}[\textbf{Proof of Theorem \ref{thm:y}, p\pageref{thm:y}}]
  \label{prf:y}
  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\yu}$ and $\beta_{\yl}$,
  \begin{align*}
    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid \yu, n, m, s, N)}{p(l \mid \yl, n, m, s, N)}} \\
    &= \frac{B(l + n \yu + s, m - l + n (1 - \yu) + N - s) B(n \yl + s, n (1 - \yl) + N - s)}
            {B(n \yu + s, n (1 - \yu) + N - s) B(l + n \yl + s, m - l + n (1 - \yl) + N - s)} \\
    &= \frac{\Gamma(l + n \yu + s) \Gamma(m - l + n (1 - \yu) + N - s) \Gamma(n \yl + s) \Gamma(n (1 - \yl) + N - s)}
            {\Gamma(l + n \yl + s) \Gamma(m - l + n (1 - \yl) + N - s) \Gamma(n \yu + s) \Gamma(n (1 - \yu) + N - s)} \\
    &= \left\{ \begin{aligned}
         \frac{\prod_{x=0}^{m-1} (x + n (1 - \yu) + N - s)}
              {\prod_{x=0}^{m-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } l=0 \\
         \frac{\prod_{x=0}^{l-1} (x + n \yu + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yu) + N - s)}
              {\prod_{x=0}^{l-1} (x + n \yl + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } 0<l<m \\
         \frac{\prod_{x=0}^{m-1} (x + n \yu + s)}
              {\prod_{x=0}^{m-1} (x + n \yl + s)} &\quad\mbox{ for } l=m
       \end{aligned} \right.
  \end{align*}
  since $\Gamma(x+1)=x \Gamma(x)$.

  Thus,
  \begin{align*}
    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
      \frac{(l + n \yu) (m - l - 1 + n (1 - \yl) + N - s)}
           {(l + n \yl) (m - l - 1 + n (1 - \yu) + N - s)} \\
    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
  \end{align*}

  Hence, $\mathcal{L}(\cdot)$ is monotone increasing for $0 < \yl < \yu < 1$, so that $\beta_{\yu}$ is larger than or equal to $\beta_{\yl}$ in monotone likelihood ratio order ($\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl}$).  But, $\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl} \implies \beta_{\yu} \ge_\mathrm{st} \beta_{\yl}$ (\cite[Theorem 1.C.1, p.43]{shaked2007}) giving the required result.
\end{proof}

\begin{proof}[\textbf{Proof of Theorem \ref{thm:n}, p\pageref{thm:n}}]
  \label{prf:n}
  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\nu}$ and $\beta_{\nl}$,
  \begin{align*}
    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)}} \\
    &= \frac{B(l + \nu y + s, m - l + \nu (1 - y) + N - s) B(\nl y + s, \nl (1 - y) + N - s)}
            {B(\nu y + s, \nu (1 - y) + N - s) B(l + \nl y + s, m - l + \nl (1 - y) + N - s)} \\
    &= \frac{\Gamma(l + \nu y + s) \Gamma(m - l + \nu (1 - y) + N - s)}
            {\Gamma(l + \nl y + s) \Gamma(m - l + \nl (1 - y) + N - s)} \\
    &\quad \times \frac{\Gamma(\nl y + s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu+N) \Gamma(m+\nl+N)}
                       {\Gamma(\nu y + s) \Gamma(\nu (1 - y) + N - s)\Gamma(\nl+N) \Gamma(m+\nu+N)} \\
    &= \left\{ \begin{aligned}
         \frac{\prod_{x=0}^{m-1} (x + \nu (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nl + N)}
              {\prod_{x=0}^{m-1} (x + \nl (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=0 \\
         \frac{\prod_{x=0}^{l-1} (x + \nu y + s) \prod_{x=0}^{m-l-1} (x + \nu (1 - y) + N - s)}
              {\prod_{x=0}^{l-1} (x + \nl y + s) \prod_{x=0}^{m-l-1} (x + \nl (1 - y) + N - s)} \\
         \quad \times \frac{\prod_{x=0}^{m-1} (x + \nl + N)}{\prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } 0<l<m \\
         \frac{\prod_{x=0}^{m-1} (x + \nu y + s) \prod_{x=0}^{m-1} (x + \nl + N)}
              {\prod_{x=0}^{m-1} (x + \nl y + s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=m
       \end{aligned} \right.
  \end{align*}
  since $\Gamma(x+1)=x \Gamma(x)$.

  Thus,
  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
      \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
           {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
  \]

  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
  for the other parameters, so that necessary conditions for
  monotonicity (either increasing or decreasing) must be established.
  We require,
  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
     >1
  \]
  After extensive routine algebra, this can be conveniently expressed as
  \begin{align*}
    (\nu - \nl)[y (N + m) - s - y] - l (\nu - \nl)>0.
  \end{align*}
  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
  Thus, for monotonicity to hold for all $l$, we require
  \begin{align*}
    (\nu - \nl)[y (N + m) - s - y] - m (\nu - \nl) &>0 \\
    \implies (\nu - \nl)[y (N + m - 1) - s - y] &>0
  \end{align*}
  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
  likelihood ratio only when \[ y (N + m - 1) - s - y > 0. \]  Likewise 
  the likelihood ratio is only monotonically decreasing when
  \[ y (N + m - 1) - s - y < 0. \]
  Thus,
  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and 
  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
  by \cite[Theorem 1.C.1, p.43]{shaked2007}.
\end{proof}

\section{Software details}
\label{ap:software}

>>>>

@@

Based on expert assumptions for component failure distributions and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

%Our imprecise probability approach leads to sets of system reliability functions,
%where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
%reflects the precision of the reliability estimate:
%a short range will indicate that we can quantify the reliability of the system quite precisely,
%while a large range will indicate that our (probabilistic) knowledge is rather shaky --
%remember that the reliability function is in essence a collection of probability statements.
Our imprecise probability approach leads, for each $t$ in some grid of time points ${\cal T}$,
to a posterior predictive probability interval for the event that the system will function at time $t$.
The width of these intervals reflects the precision of the probability statement:
a short range will indicate that we can quantify the system functioning probability quite precisely,
while a large range will indicate that our (probabilistic) knowledge is indeterminate.

@@

As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
ultimately conveying a false sense of certainty
by communicating that we can quantify the reliability of the system quite precisely when in fact we cannot do so.
In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.

@@

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
Like \citet{CCMA14}, we will utilize the monotonicity of the survival signature for coherent systems
to simplify computations.

@@

To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.

To see this,
remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
%the posterior parameter set bounds are the transformed prior parameter set bounds,
%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
%
Now, a higher posterior expected functioning probability means
higher probability for many components out of $m_k$ surviving,
i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
such that the cmfs for different values of $\yktn$ do not cross each other.
This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
We therefore have
%
%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
%keeping all other component type expressions fixed.
%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
\begin{align}
\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
 &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \nonumber \\
 &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,. \label{eq:LwrSysPost}
\end{align}
In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
%***How to choose the sets of priors for the survival function of type $k$ components,
%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***

@@

The survival signature and its use for uncertainty quantification for system
reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
to reflect uncertainty about system functioning for known states of its components, with a further
generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
survival signature to multi-state systems such that it again summarizes the structure function
in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.

***Extend the model to deal with right-censored observations which are common in the reliability setting.
The minimal assumption that a component can either fail immediately after censoring or live forever
will be simple to implement but will lead to high imprecision,
whereas assuming exchangeability with other surviving components at moment of censoring
will be more complex to accomodate but will lead to less imprecision.
This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.

@@

\section*{Appendix}
\appendix
\renewcommand*{\thesection}{\Alph{section}}
\section{Software details}
\label{ap:software}
